### 2022-10-14 preprint.tex
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@230beaa0261730b22ad4cadb32c74b1331cb84d4 🚀

\marginpar{\vskip 1em\flushright
{\small{\bfseries Keywords}:\par
pandoc\\pandoc-crossref\\github actions\\}
}

@@

Here, we have demonstrated that we expect false-negatives in species
interaction datasets purely due to the distribution of abundances within
a community. Positive associations between species occurrence (Cazelles
\emph{et al.} 2016) can increase the realized false-negative rate if the
sampling effort is limited, and we have presented evidence of this
non-random structure of co-occurrence in two sets of
spatially-replicated ecological network samples. We have also shown that
false-negatives can cause varying responses in our measurements of
network properties and further could impact our ability to reliably
predict interactions, which highlights the need for further research
into methods for correcting this bias in existing data (Stock \emph{et
al.} 2017). A brief caveat here is that we do not consider the rate of
false-positives---in large part false-positives can be explained by
misidentification of species, although this could be a relevant
consideration in some cases.

What does the future hold for this research? A better understanding of
how false-negatives impact our analyses and prediction of ecological
networks is a practical necessity. False-negatives could pose a problem
for many forms of inference in network ecology. For example, if we aim
to measure structural or dynamic stability of a network, or to infer
indirect interactions (Williams \emph{et al.} 2002), these estimates
could be prone to error if the observed network is not sampled
``enough''. What exactly ``enough'' means is then specific to the
application, and should be assessed via methods like those here when
designing samples. Further, predictions about network rewiring (Thompson
\& Gonzalez 2017) due to a changing climate could be error-prone without
accounting for interactions that have not been observed but that still
may become climatically infeasible.

This highlights the need for a quantitatively robust approach samples
design: for interactions (Jordano 2016b) and otherwise (Carlson \emph{et
al.} 2020). The primary takeaway is that when planning the sampling
effort across sites, it is necessary to take both the size of the
species pool into account. Further, simulating the process of
observation could be a powerful tool for planing study design which
takes relative abundance into account, and provide a null baseline for
detection of interaction strength. A model similar to that here can and
should be used to provide a neutral expectation of true-negative
probability given a number of observations of individuals at a given
place and time.

As we derive from fig.~\ref{fig:negativebinom}, we can never guarantee
there are no false-negatives in data. In recent years, there has been
interest toward explicitly accounting for false-negatives in models
(Stock \emph{et al.} 2017; Young \emph{et al.} 2021), and toward a
predictive approach toward interactions ---rather than expect that our
samples can fully capture all interactions, we know that some
interactions between species will not be observed due to finite sampling
capacity, and instead we must impute the true metaweb of interactions
given a set of samples (Strydom \emph{et al.} 2021). As a result, better
predictive approaches are needed for interaction networks (Strydom
\emph{et al.} 2021), and building models that explicitly account for
observation error is a necessary step forward for predictive ecological
models (Johnson \& Larremore 2021; Young \emph{et al.} 2021). Neural
networks, like the one used to predict interactions in the above
section, have been used to reflect hidden states which account for
detection error in occupancy modeling (Joseph 2020), and could be
integrated in the predictive models of the future.

A better conceptual framework for designing surveys and monitoring
networks, and incorporating sequential observations over time is clearly
needed (Carlson \emph{et al.} 2020), combined with a meta-analysis of
sampling effort and taxonomic resolution in existing data. Incorporating
a better understanding of sampling effects and bias on both the future
design of biodiversity monitoring systems, and the predictive models we
wish to apply to this data, is imperative in making actionable
predictions about the future of ecological interactions on our planet.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Becker2021OptPre}{}}%
Becker, D.J., Albery, G.F., Sjodin, A.R., Poisot, T., Bergner, L.M.,
Dallas, T.A., \emph{et al.} (2021).
\href{https://doi.org/10.1101/2020.05.22.111344}{Optimizing predictive
models to prioritize viral discovery in zoonotic reservoirs}.
\emph{bioRxiv}, 2020.05.22.111344.

\leavevmode\vadjust pre{\hypertarget{ref-Bezanson2015JulFre}{}}%
Bezanson, J., Edelman, A., Karpinski, S. \& Shah, V.B. (2015).
\href{https://arxiv.org/abs/1411.1607}{Julia: A Fresh Approach to
Numerical Computing}. \emph{arXiv:1411.1607 {[}cs{]}}.

@@

@@

@@

\leavevmode\vadjust pre{\hypertarget{ref-Connor2017UsiNul}{}}%
Connor, N., Barberán, A. \& Clauset, A. (2017).
\href{https://doi.org/10.1371/journal.pone.0176751}{Using null models to
infer microbial co-occurrence networks}. \emph{PLOS ONE}, 12, e0176751.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Giacomuzzo2021FooWeb}{}}%
Giacomuzzo, E. \& Jordán, F. (2021).
\emph{\href{https://doi.org/10.1101/2021.04.18.440319}{Food web
aggregation: Effects on key positions}} (Preprint). Ecology.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Hadfield2014TalTwo}{}}%
Hadfield, J.D., Krasnov, B.R., Poulin, R. \& Nakagawa, S. (2014).
\href{https://doi.org/10.1086/674445}{A Tale of Two Phylogenies:
Comparative Analyses of Ecological Interactions}. \emph{The American
Naturalist}, 183, 174--187.

\leavevmode\vadjust pre{\hypertarget{ref-Johnson2021BayEst}{}}%
Johnson, E.K. \& Larremore, D.B. (2021).
\href{https://doi.org/10.1101/2021.07.06.451319}{Bayesian estimation of
population size and overlap from random subsamples}. \emph{bioRxiv},
2021.07.06.451319.

\leavevmode\vadjust pre{\hypertarget{ref-Jordano2016ChaEco}{}}%
Jordano, P. (2016a).
\href{https://doi.org/10.1371/journal.pbio.1002559}{Chasing Ecological
Interactions}. \emph{PLOS Biology}, 14, e1002559.

\leavevmode\vadjust pre{\hypertarget{ref-Jordano2016SamNet}{}}%
Jordano, P. (2016b).
\href{https://doi.org/10.1111/1365-2435.12763}{Sampling networks of
ecological interactions}. \emph{Functional Ecology}.

@@

@@

\leavevmode\vadjust pre{\hypertarget{ref-Makiola2020KeyQue}{}}%
Makiola, A., Compson, Z.G., Baird, D.J., Barnes, M.A., Boerlijst, S.P.,
Bouchez, A., \emph{et al.} (2020).
\href{https://doi.org/10.3389/fenvs.2019.00197}{Key Questions for
Next-Generation Biomonitoring}. \emph{Frontiers in Environmental
Science}, 7.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Nielsen2007EcoNet}{}}%
Nielsen, A. \& Bascompte, J. (2007).
\href{https://doi.org/10.1111/j.1365-2745.2007.01271.x}{Ecological
networks, nestedness and sampling effort}. \emph{Journal of Ecology},
95, 1134--1141.

\leavevmode\vadjust pre{\hypertarget{ref-Paine1988RoaMap}{}}%
Paine, R.T. (1988). \href{https://doi.org/10.2307/1941141}{Road Maps of
Interactions or Grist for Theoretical Development?} \emph{Ecology}, 69,
1648--1654.

\leavevmode\vadjust pre{\hypertarget{ref-Poisot2021GloKno}{}}%
Poisot, T., Bergeron, G., Cazelles, K., Dallas, T., Gravel, D.,
MacDonald, A., \emph{et al.} (2021a).
\href{https://doi.org/10.1111/jbi.14127}{Global knowledge gaps in
species interaction networks data}. \emph{Journal of Biogeography},
jbi.14127.

\leavevmode\vadjust pre{\hypertarget{ref-Poisot2021ImpMam}{}}%
Poisot, T., Ouellet, M.-A., Mollentze, N., Farrell, M.J., Becker, D.J.,
Albery, G.F., \emph{et al.} (2021b).
\href{https://arxiv.org/abs/2105.14973}{Imputing the mammalian virome
with linear filtering and singular value decomposition}.
\emph{arXiv:2105.14973 {[}q-bio{]}}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Resasco2021PlaPol}{}}%
Resasco, J., Chacoff, N.P. \& Vázquez, D.P. (2021).
\href{https://doi.org/10.1002/ecy.3359}{Plantpollinator interactions
between generalists persist over time and space}. \emph{Ecology}, 102,
e03359.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Schwarz2020TemSca}{}}%
Schwarz, B., Vázquez, D.P., CaraDonna, P.J., Knight, T.M., Benadi, G.,
Dormann, C.F., \emph{et al.} (2020).
\href{https://doi.org/10.1111/oik.07303}{Temporal scale-dependence of
plantpollinator networks}. \emph{Oikos}, 129, 1289--1302.

\leavevmode\vadjust pre{\hypertarget{ref-Stephenson2020TecAdv}{}}%
Stephenson, P. (2020).
\href{https://doi.org/10.1016/j.cosust.2020.08.005}{Technological
advances in biodiversity monitoring: Applicability, opportunities and
challenges}. \emph{Current Opinion in Environmental Sustainability}, 45,
36--41.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Strydom2021RoaPre}{}}%
Strydom, T., Catchen, M.D., Banville, F., Caron, D., Dansereau, G.,
Desjardins-Proulx, P., \emph{et al.} (2021).
\emph{\href{https://doi.org/10.32942/osf.io/eu7k3}{A Roadmap Toward
Predicting Species Interaction Networks (Across Space and Time)}}
(Preprint). EcoEvoRxiv.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Williams2002TwoDeg}{}}%
Williams, R.J., Berlow, E.L., Dunne, J.A., Barabasi, A.-L. \& Martinez,
N.D. (2002). \href{https://doi.org/10.1073/pnas.192448799}{Two degrees
of separation in complex food webs}. \emph{Proceedings of the National
Academy of Sciences}, 99, 12913--12916.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Willott2001SpeAcc}{}}%
Willott, S.J. (2001).
\href{https://doi.org/10.1046/j.1365-2664.2001.00589.x}{Species
accumulation curves and the measure of sampling effort}. \emph{Journal
of Applied Ecology}, 38, 484--486.

@@

>>>>

\marginpar{\vskip 1em\flushright
{\small{\bfseries Keywords}:\par
community ecology\\network ecology\\computational ecology\\species
interactions\\spatial sampling\\simulation\\}
}

@@

Species interactions enable the persistence and functioning of
ecosystems, but our understanding of interactions is limited due to the
intrinsic difficulty of sampling. Here we have provided a null model for
the expected number of false-negatives in an interaction dataset. We
demonstrated that we expect many false-negatives in species interaction
datasets purely due to the intrinsic variation of abundances within a
community. We also, for the first time to our knowledge, measured the
strength of association between co-occurrence and interactions (Cazelles
\emph{et al.} 2016) across many empirical systems for the first time,
and found that these positive associations are both very common, and
showed algebraically that they increase the realized FNR. We have also
shown that false-negatives could further impact our ability to both
predict interactions and infer properties of the networks, which
highlights the need for further research into methods for correcting
this bias in existing data.

A better understanding of how false-negatives impact our inference of
network structure and dynamics is prediction of ecological networks by
both using information about individual species interactions and the
structure of metawebs on large scales is a practical necessity.
False-negatives could pose a problem for many forms of inference in
network ecology. For example, inferring the structural or dynamic
stability of a network could be prone to error if the observed network
is not sampled ``enough''. What exactly ``enough'' means is then
specific to the application, and should be assessed via methods like
those here when designing samples. Further, predictions about network
rewiring (Thompson \& Gonzalez 2017) due to range shifts in response to
climate change could be error-prone without accounting for interactions
that have not been observed but that still may become climatically
infeasible. As is evident from Figure 1(A), we can never guarantee there
are no false-negatives in data. In recent years, there has been interest
toward explicitly accounting for false-negatives in models (Stock
\emph{et al.} 2017; Young \emph{et al.} 2021), and a predictive approach
to networks---rather than expecting our samples to fully capture all
interactions (Strydom \emph{et al.} 2021). As a result, better models
for predicting interactions are needed for interaction networks. This
includes explicitly accounting for observation error (Johnson \&
Larremore 2021)---certain classes of models have been used to reflect
hidden states which account for detection error in occupancy modeling
(Joseph 2020), and could be integrated in the predictive models of
interactions in the future.

A brief caveat here is that we do not consider the rate of
false-positives---in large part false-positives can be explained by
misidentification of species, although this could be a relevant
consideration in some cases. The same logic that we apply to
false-negatives could easily be applied to false-positives, e.g.~that we
can be much more confident that an interaction is a true positive if we
have observed it 50 times rather than only once, and we could similarly
model this using the geometric distribution as in
fig.~\ref{fig:geometric}(A). However, because ecological networks are so
sparse, there are far more negatives than positives in the dataset, and
therefore likely to be far more false-negatives than false-positives in
absolute terms.

This work has several practical consequences for the design of
interaction samples. Simulating the process of observation could be a
powerful tool for estimating the sampling effort required by a study
that takes relative abundance into account, and provides a null baseline
for expected FNR. It is necessary to take the size of the species pool
into account when deciding how many total samples is sufficient for an
``acceptable'' FNR (fig.~\ref{fig:geometric}(C \& D)). Further the
spatial and temporal turnover of interactions means any approach to
sampling prioritization must be spatiotemporal. We demonstrated earlier
that observed negatives outside of the range of both species aren't
informative, and therefore using species distribution models could aid
in this spatial prioritization of sampling sites.

Our work highlights the need for a quantitatively robust approach to
sampling design, both for interactions (Jordano 2016) and all other
aspects of biodiversity (Carlson \emph{et al.} 2020). As anthropogenic
forces create rapid shifts in our planet's climate and biosphere, this
is an imperative to maximize the amount of ecological information we get
in our finite samples, and make our inferences and decisions based on
this data as robust as possible. Where we choose to sample, and how
often we choose to sample there, has strong impacts on the inferences we
make from data. Incorporating a better understanding of sampling effort
and bias to the design of biodiversity monitoring systems, and the
inference and predictive models we apply to this data, is imperative in
understanding how biodiversity is changing, and making actionable
forecasts about the future of ecological interactions on our planet.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Bascompte2007PlaMut}{}}%
Bascompte, J. \& Jordano, P. (2007).
\href{https://doi.org/10.1146/annurev.ecolsys.38.091206.095818}{Plant-Animal
Mutualistic Networks: The Architecture of Biodiversity}. \emph{Annual
Review of Ecology, Evolution, and Systematics}, 38, 567--593.

\leavevmode\vadjust pre{\hypertarget{ref-Becker2021OptPre}{}}%
Becker, D.J., Albery, G.F., Sjodin, A.R., Poisot, T., Bergner, L.M.,
Dallas, T.A., \emph{et al.} (2021).
\href{https://doi.org/10.1101/2020.05.22.111344}{Optimizing predictive
models to prioritize viral discovery in zoonotic reservoirs}.

\leavevmode\vadjust pre{\hypertarget{ref-Bezanson2015JulFre}{}}%
Bezanson, J., Edelman, A., Karpinski, S. \& Shah, V.B. (2015).
\href{https://doi.org/10.48550/arXiv.1411.1607}{Julia: A Fresh Approach
to Numerical Computing}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Blaom2020MljJul}{}}%
Blaom, A.D., Kiraly, F., Lienart, T., Simillides, Y., Arenas, D. \&
Vollmer, S.J. (2020). \href{https://doi.org/10.21105/joss.02704}{MLJ: A
Julia package for composable machine learning}. \emph{Journal of Open
Source Software}, 5, 2704.

@@

\leavevmode\vadjust pre{\hypertarget{ref-CaraDonna2017IntRew}{}}%
CaraDonna, P.J., Petry, W.K., Brennan, R.M., Cunningham, J.L.,
Bronstein, J.L., Waser, N.M., \emph{et al.} (2017).
\href{https://doi.org/10.1111/ele.12740}{Interaction rewiring and the
rapid turnover of plantpollinator networks}. \emph{Ecology Letters}, 20,
385--394.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Closs1994SpaTem}{}}%
Closs, G.P. \& Lake, P.S. (1994).
\href{https://doi.org/10.2307/2937053}{Spatial and Temporal Variation in
the Structure of an Intermittent-Stream Food Web}. \emph{Ecological
Monographs}, 64, 1--21.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Giacomuzzo2021FooWeb}{}}%
Giacomuzzo, E. \& Jordán, F. (2021).
\href{https://doi.org/10.1111/oik.08541}{Food web aggregation: Effects
on key positions}. \emph{Oikos}, 130, 2170--2181.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Hadfield2014TalTwo}{}}%
Hadfield, J.D., Krasnov, B.R., Poulin, R. \& Nakagawa, S. (2014).
\href{https://doi.org/10.1086/674445}{A Tale of Two Phylogenies:
Comparative Analyses of Ecological Interactions.} \emph{The American
Naturalist}, 183, 174--187.

\leavevmode\vadjust pre{\hypertarget{ref-Havens1992ScaStr}{}}%
Havens, K. (1992).
\href{https://doi.org/10.1126/science.257.5073.1107}{Scale and Structure
in Natural Food Webs}. \emph{Science}, 257, 1107--1109.

\leavevmode\vadjust pre{\hypertarget{ref-Johnson2021BayEst}{}}%
Johnson, E.K. \& Larremore, D.B. (2021).
\href{https://doi.org/10.1101/2021.07.06.451319}{Bayesian estimation of
population size and overlap from random subsamples}.

\leavevmode\vadjust pre{\hypertarget{ref-Jordano2016SamNet}{}}%
Jordano, P. (2016).
\href{https://doi.org/10.1111/1365-2435.12763}{Sampling networks of
ecological interactions}. \emph{Functional Ecology}, 30, 1883--1893.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Khoshraftar2022SurGra}{}}%
Khoshraftar, S. \& An, A. (2022).
\href{https://doi.org/10.48550/arXiv.2204.01855}{A Survey on Graph
Representation Learning Methods}.

\leavevmode\vadjust pre{\hypertarget{ref-Koleff2003MeaBet}{}}%
Koleff, P., Gaston, K.J. \& Lennon, J.J. (2003).
\href{https://doi.org/10.1046/j.1365-2656.2003.00710.x}{Measuring beta
diversity for presenceabsence data}. \emph{Journal of Animal Ecology},
72, 367--382.

\leavevmode\vadjust pre{\hypertarget{ref-Kopelke2017FooStr}{}}%
Kopelke, J.-P., Nyman, T., Cazelles, K., Gravel, D., Vissault, S. \&
Roslin, T. (2017). \href{https://doi.org/10.1002/ecy.1832}{Food-web
structure of willow-galling sawflies and their natural enemies across
Europe}. \emph{Ecology}, 98, 1730--1730.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Makiola2020KeyQue}{}}%
Makiola, A., Compson, Z.G., Baird, D.J., Barnes, M.A., Boerlijst, S.P.,
Bouchez, A., \emph{et al.} (2020). Key Questions for Next-Generation
Biomonitoring. \emph{Frontiers in Environmental Science}, 7.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Niedballa2019AssAna}{}}%
Niedballa, J., Wilting, A., Sollmann, R., Hofer, H. \& Courtiol, A.
(2019). \href{https://doi.org/10.1002/rse2.107}{Assessing analytical
methods for detecting spatiotemporal interactions between species from
camera trapping data}. \emph{Remote Sensing in Ecology and
Conservation}, 5, 272--285.

\leavevmode\vadjust pre{\hypertarget{ref-Poisot2022GuiPre}{}}%
Poisot, T. (2022).
\href{https://doi.org/10.32942/osf.io/aty7n}{Guidelines for the
prediction of species interactions through binary classification}.

\leavevmode\vadjust pre{\hypertarget{ref-Poisot2021GloKno}{}}%
Poisot, T., Bergeron, G., Cazelles, K., Dallas, T., Gravel, D.,
MacDonald, A., \emph{et al.} (2021).
\href{https://doi.org/10.1111/jbi.14127}{Global knowledge gaps in
species interaction networks data}. \emph{Journal of Biogeography}, 48,
1552--1563.

\leavevmode\vadjust pre{\hypertarget{ref-Poisot2022NetEmb}{}}%
Poisot, T., Ouellet, M.-A., Mollentze, N., Farrell, M.J., Becker, D.J.,
Brierly, L., \emph{et al.} (2022).
\href{https://doi.org/10.48550/arXiv.2105.14973}{Network embedding
unveils the hidden interactions in the mammalian virome}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Ponisio2017OppAtt}{}}%
Ponisio, L.C., Gaiarsa, M.P. \& Kremen, C. (2017).
\href{https://doi.org/10.1111/ele.12821}{Opportunistic attachment
assembles plantpollinator networks}. \emph{Ecology Letters}, 20,
1261--1272.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Song2022GenDri}{}}%
Song, C., Simmons, B.I., Fortin, M.-J. \& Gonzalez, A. (2022).
\href{https://doi.org/10.1371/journal.pcbi.1010302}{Generalism drives
abundance: A computational causal discovery approach}. \emph{PLOS
Computational Biology}, 18, e1010302.

\leavevmode\vadjust pre{\hypertarget{ref-Stephenson2020TecAdv}{}}%
Stephenson, P. (2020).
\href{https://doi.org/10.1016/j.cosust.2020.08.005}{Technological
advances in biodiversity monitoring: Applicability, opportunities and
challenges}. \emph{Current Opinion in Environmental Sustainability},
Open Issue 2020 Part A: Technology Innovations and Environmental
Sustainability in the Anthropocene, 45, 36--41.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Strydom2021RoaPre}{}}%
Strydom, T., Catchen, M.D., Banville, F., Caron, D., Dansereau, G.,
Desjardins-Proulx, P., \emph{et al.} (2021).
\href{https://doi.org/10.1098/rstb.2021.0063}{A roadmap towards
predicting species interaction networks (across space and time)}.
\emph{Philosophical Transactions of the Royal Society B: Biological
Sciences}, 376, 20210063.

@@

@@

\leavevmode\vadjust pre{\hypertarget{ref-Willott2001SpeAcc}{}}%
Willott, S.j. (2001).
\href{https://doi.org/10.1046/j.1365-2664.2001.00589.x}{Species
accumulation curves and the measure of sampling effort}. \emph{Journal
of Applied Ecology}, 38, 484--486.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Zhang2019GraCon}{}}%
Zhang, S., Tong, H., Xu, J. \& Maciejewski, R. (2019).
\href{https://doi.org/10.1186/s40649-019-0069-y}{Graph convolutional
networks: A comprehensive review}. \emph{Computational Social Networks},
6, 11.
